\sysfull

### 2018-04-16 paper/systemdescription.tex
system descripton updates

\begin{wrapfigure}{t!}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/graffle/overview.pdf}
	\caption{\sys top-level view. \textcolor{red}{redraw the figure: change font type}}
	\label{fig:system_overview}
\end{wrapfigure}

@@

@@

\textbf{\sys Task Coalescing Manager.} \sys relies on its task coalescing manager to dynamically {\em coalesce} statically\hyp{}defined tasks to avoid inessential overheads associated with completing tasks. By default, tasks run in a sequence and each task commits its task-shared state as it completes.  The time and energy cost of a task's commit is unnecessary if the task and its successor both complete without a power failure. The key insight that \sys leverages is that the first task could have deferred its commit to the second task. {\em coalescing} tasks by deferring the first commit avoids the fixed cost of the first commit (task transitioning overheads). Coalescing also amortizes per-variable commit cost, committing each location accessed by both tasks only after the second task, rather than once per task. \textcolor{red}{\sys's coalescing manager is an \emph{energy-aware manager}. It uses the recent execution history---pure software technique---as a metric to estimate the amount of the available energy and to set the adequate coalesced task size accordingly. This fundamental feature prevents \sys from blind coalesced task adaptation which may result in a repeated power failure problem. For example, If \sys enlarges the coalesced task size by $x$ static tasks on a coalesced task completion and reduces it by the same number of static tasks on a power reboot, then \sys may need to reboot, for instance, 10 times to reduce a coalesced task size from 10 to one, when $x=1$}. Details of coalescing are presented in Section~\ref{sec:task_coalescing}.

\textbf{\sys Task Downscaling Manager.} \textcolor{red}{\sys's downscaling manager is responsible for preserving the forward progress when \sys repeatedly fails on a single static task. The downscaling manager utilizes a timer-based technique and relies on the virtual memory manager to gain a full \emph{flexibility} on where to split a task. These features distinguish \sys task splitting technique from the traditional checkpointing. A checkpointing system that uses voltage threshold to place a checkpoint might cause a program to crash if the checkpoint happened to be placed between a peripheral initialization and its call. If a programmer disables interrupts between the peripheral initialization and the call, the program may fail indefinitely to progress since the checkpoint may only be deferred. The \sys task downscaling manager, on the other hand,  triggers  a \emph{partial commit} faster than the previous one on a repeated failure to guarantee forward progress. Details of task downscaling are presented in Section~\ref{sec:task_downsizing}.}

\textbf{\sys Virtual Memory Manager.} \sys is able to efficiently coalesce tasks because of its efficient virtual memory manager, which is described in Section~\ref{sec:memory_virtualization}. \sys's memory manager paginates memory and ensures that data in a page remain consistent despite power interruptions. \sys allows a task to manipulate data in a volatile copy of a page only. Pages swap between volatile and non-volatile memory, depending on the capacity of the volatile memory and the program's access pattern. \sys tracks a task's memory accesses efficiently at page granularity (rather than using, e.g., costly word-granular tracking). When a task ends, each page it accessed commits from volatile memory (or from a non-volatile swap region for dirty pages) back to the non-volatile main memory. Pages efficiently, atomically commit using a two-phase commit procedure accelerated using hardware support for direct memory access (DMA). Details of Virtual Memory Manager are presented in Section~\ref{sec:memory_virtulaization}.

>>>>

@@

\begin{wrapfigure}{t!}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/graffle/overview.pdf}
	\caption{\sys top-level view. \sys is composed of two core components: \emph{Task Scheduler} and \emph{Memory Manager}.\todo{Redraw figure to map new terms}{Carlo}}
	\label{fig:system_overview}
\end{wrapfigure}

@@

\textbf{\sys Task Coalescing Manager.} \sys relies on its task coalescing manager to dynamically {\em coalesce} statically\hyp{}defined tasks to avoid inessential overheads associated with completing tasks. By default, tasks run in a sequence and each task commits its task-shared state as it completes. The time and energy cost of a task's commit is unnecessary if the task and its successor both complete without a power failure. The key insight that \sys leverages is that the first task could have deferred its commit to the second task. {\em Coalescing} tasks by deferring the first commit avoids the fixed cost of the first commit (task transitioning overheads). Coalescing also amortizes per-variable commit cost, committing each location accessed by both tasks only after the second task, rather than once per task.

\sys's coalescing manager is an \emph{energy-aware} and \emph{software-based only} manager in a sense it uses the recent execution history as a metric to estimate the amount of the available energy to set the adequate coalesced task size accordingly. This fundamental feature prevents \sys from blind coalesced task adaptation which may result in a repeated power failure problem. For example, If \sys enlarges the coalesced task size by $x$ static tasks on a coalesced task completion and reduces it by the same number of static tasks on a power reboot, then \sys may need to reboot, for instance, ten times to reduce a coalesced task size from ten to one, when $x=1$. Details of coalescing will be given in Section~\ref{sec:task_coalescing}.

\textbf{\sys Task Downscaling Manager.} \sys's task downscaling manager is responsible for preserving the forward progress when \sys repeatedly fails on a single static task. The downscaling manager utilizes a timer-based technique and relies on the virtual memory manager to gain a full \emph{flexibility} on where to split a task. These features distinguish \sys task splitting technique from the traditional checkpointing. A checkpointing system that uses voltage threshold to place a checkpoint might cause a program to crash if the checkpoint happened to be placed between a peripheral initialization and its call. If a programmer disables interrupts between the peripheral initialization and the call, the program may fail indefinitely to progress since the checkpoint may only be deferred. The \sys task downscaling manager, on the other hand, triggers a \emph{partial commit} faster than the previous one on a repeated failure to guarantee forward progress. Details of task downscaling will be given in Section~\ref{sec:task_downsizing}.

\textbf{\sys Virtual Memory Manager.} \sys is able to efficiently coalesce tasks because of its efficient virtual memory manager. \sys's memory manager paginates memory and ensures that data in a page remain consistent despite power interruptions. \sys allows a task to manipulate data in a volatile copy of a page only. Pages swap between volatile and non-volatile memory, depending on the capacity of the volatile memory and the program's access pattern. \sys tracks a task's memory accesses efficiently at page granularity (rather than using, e.g., costly word-granular tracking). When a task ends, each page it accessed commits from volatile memory (or from a non-volatile swap region for dirty pages) back to the non-volatile main memory. Pages efficiently, atomically commit using a two-phase commit procedure accelerated using hardware support for direct memory access (DMA). Details of Virtual Memory Manager are will be given in Section~\ref{sec:memory_virtulaization}.
